Reproduce anaylses of Beninca et al (2008)

### 2016-03-23 code/report.Rmd
remove some possibly interfering code

Only keep the upper triangle of the cor.pvals matrix:
```{r}
#for(i in 1:10){
#  for(j in 1:10){
#  cor.coefs[i,j] <- ifelse(i<j, cor.coefs[i,j], NA)
#}}
```

@@

Only keep the upper triangle of the cor.pvals matrix:
```{r}
#for(i in 1:10){
#  for(j in 1:10){
#  cor.pvals[i,j] <- ifelse(i<j, cor.pvals[i,j], NA)
#}}
```

@@

Cosmetic work on the table:
```{r}
oo <- c(10, 9, 8, 11, 12, 6, 5, 3, 4, 2)
cor.coefs <- cor.coefs[oo,oo]
cor.cp <- cor.cp[oo,oo]
for(i in 1:length(cor.cp[1,]))
  for(j in 1:i)
  cor.cp[i,j] <- ""
#sn <- c("Bacteria", "Harps", "Ostr", "N", "P", "Picophyt", "Nanophyt", "Rotifers", "Protozoa", "Calanoids")
sn <- substr(rownames(cor.cp), 1, 4)
sn[4:5] <- c("N", "P")
dimnames(cor.cp) <- list(sn, sn)
```

>>>>

@@

@@

Cosmetic work on the table:
```{r}
dim(cor.coefs) ## should be 12,12
oo <- c(10, 9, 8, 11, 12, 6, 5, 3, 4, 2)
cor.coefs <- cor.coefs[oo,oo]
cor.cp <- cor.cp[oo,oo]
for(i in 1:length(cor.cp[1,]))
  for(j in 1:i)
  cor.cp[i,j] <- ""
#sn <- c("Bacteria", "Harps", "Ostr", "N", "P", "Picophyt", "Nanophyt", "Rotifers", "Protozoa", "Calanoids")
sn <- substr(rownames(cor.cp), 1, 4)
sn[4:5] <- c("N", "P")
dimnames(cor.cp) <- list(sn, sn)
```
